Seminar Paper

### 2021-11-18 paper.tex
Token based replay

>>>>

\subsubsection{Token based Replay}

The easiest conformance checking method, both conceptually and algorithmically is probably Token based replay.
The intuition behind token based replay is to replay an observed trace on a process model, specifically a petri net, and to determine where problems occur.

This is done by keeping track of four numbers: \emph{\underline{p}roduced}, \emph{\underline{c}onsumed}, \emph{\underline{m}issing} and \emph{\underline{r}emaining} tokens during replay.
According to the semantics of petri nets, whenever an action is fired it consumes one token from all input places and produces one token in each output place.
However since we are dealing with possibly non-conformant trace, it is possible that a trace contains actions, that are not enabled in the model at that point in time.
In this case a missing token is added to all input places, that did not contain a token, and the $m$ counter is incremented by the according amount.
Conversely it might also happen, that a trace can be replayed, but that there are stray tokens left in the petri net after the replay. 
At the end of the replay the sum of all leftover tokens makes up the $r$ counter.
Both missing and remaining tokens signal deviation from the process model, but both of these numbers are dependant on the length of traces.
The longer a trace is the more actions will be taken, the more tokens will be produced, and the more chances there are for tokens to be missing or remaining.
Importantly a trace where half the produced tokens were never consumed, i.e. remained, should intuitively have a lower fitness than one where only a quarter of produced tokens remained.
Of course the same relationship holds for the other two counters $m$ and $c$.
Then one very naturally arrives at a trace fitness defined as 
\begin{equation}
fitness(σ,N) = \frac{1}{2}(1-\frac{m_{N,σ}}{c_{N,σ}})+\frac{1}{2}(1-\frac{r_{N,σ}}{p_{N,σ}})
\end{equation}
, where $x_{N,σ}$ is the counter when replaying trace $σ$ on petri net $N$.
Often one does not just want to determine the fitness of one trace but a complete log, then this definition can be extended to 
\begin{equation}
	fitness(L,N) = \frac{1}{2}(1-\frac{\sum_{σ\in L}m_{N,σ}}{\sum_{σ\in L}c_{N,σ}})+\frac{1}{2}(1-\frac{\sum_{σ\in L}r_{N,σ}}{\sum_{σ\in L}p_{N,σ}})
\end{equation}
Note that log-fitness is not mathematically equivalent to the mean trace fitness.

\subsubsection{Alignments}
